Where and Why Does the Model Failed? A Visual Analytics Tool for Debugging and Interpreting Text Entailment Model

### 2018-02-22 paper/background.tex
add short intro

@@

\subsection{Interprebilty Challenges}
Making sense and explaining predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).

>>>>

Recently, with the wide adoption of long-short term memory
(LSTM) network and the introduction of attention mechanism,
neural network based model have
dominated nearly all linguistic tasks and thoroughtly refreshed the
baseline performances.
%
However, the disruptive advance also brings enormous challenges.
Due to the opaque nature of the neural network model, interpret and making sense
of many internal model mechanisms can be extremely challenging.
%
Many methods has been proprosed

The discrete nature of words and
sentences presents additional challenge for make sense of the model.
%

@@

\subsection{Interprebilty Challenges}

The introduction of attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences. The new challenges

Making sense and explaining predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).

### 2018-02-22 paper/paper_entailVis.tex
add short intro

%% Paper title.
\title{Where and Why Does the Model Failed? A Visual Analytics Tool for Debugging, Tunning, and Interpreting Text Entailment Model}

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances of deep learning, neural network based models have reset
the state-of-the-art for nearly all linguistic tasks in natural language
processing. The disruptive advance also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and
difficult to interpret mechanism~cite{}. In this work, we use textual
entailment task as an example to illustrate how a flexible visualization
system can help NLP researchers quickly identify the potential limitation of
a models and probe the model inner states for interpreting key mechanism
such as attention.
} % end of abstract

@@

%% the only exception to this rule is the \firstsection command
\input{intro_entailVis.tex}
\input{relatedWorks_entailVis.tex}
\input{background.tex}
% \input{tasks.tex}
\input{perturbation.tex} % how to do the perturbation
\input{attention.tex} % how to encode the information
\input{application.tex}
%%%%%%%%%%%%% identify errors %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% interpret attention %%%%%%%%%%%%%%%%%%%

>>>>

%% Paper title.
\title{Where and Why Does the Model Failed?  A Visual Analytics Tool for Debugging and Interpreting Text Entailment Model}

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances of deep learning, neural network based models have reset
the state-of-the-art for nearly all linguistic tasks in natural language
processing. The disruptive advance also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and
difficult to interpret mechanism~cite{}. In this work, we use textual
entailment task as an example to illustrate how a flexible visualization
system can help NLP researchers quickly identify the potential limitation of
a models and interpret the model inner states for make sense of the attention mechanism.
} % end of abstract

@@

%% the only exception to this rule is the \firstsection command
\input{intro.tex}
\input{relatedWorks.tex}
\input{background.tex}
% \input{tasks.tex}
\input{perturbation.tex} % how to do the perturbation
\input{attention.tex} % how to encode the information
\input{application.tex}
%%%%%%%%%%%%% identify errors %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% interpret attention %%%%%%%%%%%%%%%%%%%
